Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-08 paper/structureScene.tex
update section IV intro

\section{Feature design}
Before supervised or unsupervised classification, it is beneficial to process scattering coefficients with feature transformations that improve invariance, normality, or generalization power. 
This section reviews \ml{several means of achieving those goals:} binaural data augmentation, feature selection, logarithmic compression, standardization, and temporal integration.
\ml{The former has, to the best of our knowledge, not being considered for ASC and specific to multichannel recordings}, whereas the next ones would also apply to many other kinds of data.

@@

\ml{Superbe section !!}

>>>>

\section{Feature design}
Before supervised or unsupervised classification, it is beneficial to process scattering coefficients with feature transformations that improve invariance, normality, or generalization power. 
In this section, we review several ways of achieving these properties, namely binaural data augmentation, feature selection, logarithmic compression, standardization, and temporal integration.
The former has, to the best of our knowledge, not being considered for ASC and is specific to multichannel recordings, whereas the next ones would also apply to many other kinds of data.

@@
